The problem and promise of scale in multilayer networks

### 2019-09-26 paper/table1.Rmd
use csv to build table 1

|               | Spatial                                                           | Net of nets                                      | Interspecific                                              |
|---------------|-------------------------------------------------------------------|--------------------------------------------------|------------------------------------------------------------|
| layer         | spatially explicit                                                | subpops, fuzzy patches                           | dif species                                                |
| node          | individuals                                                       | ind + nets                                       | ind + species nets                                         |
| inter edges   | to self                                                           | to nets                                          | to species                                                 |
| intra edges   | association to other                                              | association                                      | association                                                |
| social grain  | type of interaction, chain rule, spatsoc threshold, hyena session | for intra, see left. for inter: define community |  for intra, see left. for inter: similarity, vulnerability |
| spatial grain | resolution                                                        | patches, k=                                      | connectivity, clusters                                     |

>>>>

```{r, echo = FALSE}
library(data.table)
tab1 <- fread('table1.csv')
knitr::kable(tab1)
```
